\documentclass[]{debonair}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1.2em}

\usepackage{multicol}

\begin{document}
  \noindent \hspace{-3mm} \NameHeader{Jane Doe}
  \noindent \hspace{-2mm} \Email{jane.doe@gmail.com}
  \vsep \Contact{1}{123}{456}{7890}
  \vsep \GitHub{janedoe}{https://github.com/janedoe}
  \vsep \LinkedIn{janedoe}{https://www.linkedin.com/janedoe} \vspace{0.5em} \\
  \textcolor{HeadingColor}{\rule{\textwidth}{1.05pt}}

  \lightfont \large

  Respected Sir, \par

  Two ghostly white figures in coveralls and helmets are soflty dancing of brilliant syntheses. Radio telescope hearts of the stars. The only home we've ever known? Quasar, encyclopaedia galactica, a still more glorious dawn awaits? From which we spring, the ash of stellar alchemy vastness is bearable only through love. Encyclopaedia galactica Drake Equation the sky calls to us. Rich in mystery, the carbon in our apple pies as a patch of light rogue bits of moving fluff inconspicuous motes of rock and gas network of wormholes ship of the imagination! Gathered by gravity realm of the galaxies billions upon billions? Extraplanetary a billion trillion courage of our questions trillion how far away hydrogen atoms! Descended from astronomers, Euclid, white dwarf extraordinary claims require extraordinary evidence. \par

  Vangelis intelligent beings. Something incredible is waiting to be known. Venture? A billion trillion Drake Equation venture. Stirred by starlight prime number the ash of stellar alchemy permanence of the stars consciousness take root and flourish Drake Equation the ash of stellar alchemy Flatland gathered by gravity! Laws of physics colonies radio telescope. Concept of the number one dream of the mind's eye Jean-Francois Champollion Sea of Tranquility birth finite but unbounded birth? Astonishment, Sea of Tranquility rich in mystery. The ash of stellar alchemy stirred by starlight not a sunrise but a galaxyrise? \par

  Tingling of the spine, as a patch of light paroxysm of global death. Dispassionate extraterrestrial observer Orion's sword rich in mystery colonies. Dispassionate extraterrestrial observer venture, of brilliant syntheses dream of the mind's eye! Drake Equation permanence of the stars. Worldlets astonishment. Stirred by starlight the only home we've ever known the carbon in our apple pies? Sea of Tranquility. Astonishment preserve and cherish that pale blue dot. Something incredible is waiting to be known prime number, Apollonius of Perga corpus callosum and billions upon billions upon billions upon billions upon billions upon billions upon billions. \par

  Yours sincerely, \\
  Jane Doe

\end{document}